Supplementary Materials

### 2018-05-25 Writeup/sup_mat.tex
Update sup_mat.tex
Adding AC and FG participant exclusion info

@@

@@

>>>>

Two participants whose accuracy rates were more than 3 SD below the mean were removed from analyses, leaving 60 participants remaining for ACVS analyses. [REMOVED FOR ACCURACY: 38, 39. ALSO ONE PERSON MISSING AC DATA:32; THREE PEOPLE MISSING ALL DATA: 18, 48, 57]

@@

[ACCURACY OK BUT MISSING DATA: ONE PERSON MISSING MISSING CONJUNCTION DATA: 1; SIX PEOPLE MISSING FEATURE DATA: 31, 35, 49, 50, 51, 52; THREE PEOPLE MISSING ALL DATA: 18, 48, 57. TOTAL N = 56]

@@

[DON'T HAVE MUCH TO ADD HERE FOR EITHER ADAPTIVE CHOICE OR FORAGING THAT ISN'T ALREADY IN THE METHOD. BUT COULD SHIFT THAT INTO HERE IF YOU WANT]
